\documentclass[10pt,a4paper,oneside]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Michael Walker}
\title{Techie Bible}
\begin{document}

\maketitle{}

\section{Genesis}
In the beginning there was the Stage, and the Stage was without lights or sets, and darkness was on the faces of the actors. And the Technical Director (hereinafter referred to as the TD) said, "Let there be Lights!" and the TECHIES worked and wired, and there were lights. Spotlights and specials, areas and backlighting - yea, lights of all shapes, sizes and hues. And the TD saw the lights, that they were well aimed and focused, gelled according to the scene, and no more was there darkness on the faces of the actors. And it was good. And the evening and the morning were the First Day. 

And the TD looked upon the actors and saw that although they walked in light, they did walk upon a bare stage, and had no place to be, and the TD was moved to pity. And the TD said, "Let there be a Set!": and the TECHIES scrambled and worked, and there was a set, with platforms, wagons, stairs, and furniture of various types and sizes, each according to the need. And the actors did walk within the set, and did have a place to be. And the TD saw the set, that it was good, and the evening and the morning were the Second Day. 

And the TD saw the actors, that although they did have a place to be, they did look like fools, for they waved their hands, clutched at open air, and struck each other with nothing. And in his heart, the TD was moved to pity. And the TD said, "Let there be Props!": and the TECHIES worked feverishly and did buy and build, and there were props. And they were good, and the evening and the morning were the Third Day. 

And the Costumer looked upon the actors, and saw that they did go forth in blue jeans and the Costumer knew that this would not due. And the Costumer said, "Let there be Costumes!": and the TECHIES did cut and sew and shape, and there were costumes, each sized to the actor, according to the play, and keeping in with the role. And no more did the actors go forth in blue jeans, and the Costumer saw the costumes, that they were good, and the evening and the morning were the Fourth Day. 

And the TD watched the play, and saw that the actors did wait in silence, and was moved to pity. And the TD said, "Let there be Sound!": and the TECHIES worked and taped, and there were sounds, each according to its place and cue, all at the proper levels. And the TD heard the sounds, that they were good, and the evening and the morning were the Fifth Day. 

And lo, all these works were completed in five days, showing that if God had used sufficient TECHIES in the first place, He would have finished sooner.

\section{The Proverbs}
\textit{Behold, my son here is wisdom. Pay heed to these words, and in the days of thy play, in the hours of thy performing, thou shalt not be caught short. For truly, it is said, pay heed to the errors of others and you shall not make them yourself, and again, as we have been told from on old, to thine own self be true.}

\begin{enumerate}
\item Give not unto the actor his props before his time, for as surely as the sun does rise in the East and set in the West, he will lose or break them. 
\item When told the placement of props by the Director, write not these things in ink upon thy script for as surely as the winds blow, so shall he change his mind. 
\item Speak not in large words to actors, for they are slow of thought and are easily confused. 
\item Speak not in the language of the TECHIE to actors, for they are uninitiated, and will not perceive thy meaning. 
\item Tap not the head of a nail to drive it, but strike it firmly with thy strength. 
\item Keep holy the first performance, for afterwards you shall party. 
\item Keep holy the last performance, for afterwards you shall party. 
\item Remember always that the TD is never wrong. If appears that he is, then you obviously misunderstood him the first time. 
\item Leave not the area of the stage during the play to go and talk with the actors, for as surely as you do, you will be in danger of missing your cue and being summarily executed or worse. 
\item Beware of the actors during scene changes, for they are not like unto you and are blind in the dark. 
\item Beware of actors when flying in walls, for they will stand and watch and get crushed. 
\item Take not thy cues before their time, but wait for the proper moment to do so. 
\item Take pity on the actors, for in their roles they are as children, and must be led with gentle kindness. Thus, endeavor to speak softly and not in anger. 
\item Listen carefully to the instructions of the Director as to how he wants things done - then do it the right way. In the days of thy work, he will see thy wisdom, give himself the credit, and rejoice. 
\item And above all, get carried away not with the glow-tape, or thy stage will be like unto an airport.\
\end{enumerate}

\section{Word to the Techies}
Remember always that thou art a TECHIE, born to walk the dark places of the stage, and know the secret ways of thy equipment. To your hands it is given to mold the dreams and thoughts of they that watch, and to make the Stage a separate place and time. Seek not, as do the actors, to go forth in light upon the stage, for though they strut and talk and put on airs, their craft does truly depend on you, to shape the dreams that they would show. 

Remember also that although they depend on you, you exist only to aid them. Remember that thou art a team, for thou shalt party together. 

My friends be not deceived by deluded actors masquerading as TECHIES. Remember always the signs by which thou shalt recognize a true TECHIE: they move softly during scene changes, not stumbling or falling; they are silent backstage and are aware of what is happening; they can speak with knowledge of Tools; they respect another's job and aid where they can; they do not just stand and watch.

Amen.

\section{Exodus}
And lo, as the year begins, so is the Gaffa Tape delivered unto the TECHIES, who do revere and worship the Gaffa. And, soon, does the Gaffa Tape leave the store, to be used by the TECHIES in pursuit of excellence in their techie activities, and also in various activites with fair TECHIE maidens. And, the head TECHIES do soon become worried at the amount of Gaffa used, for while much use of Gaffa does surely lead to a higher plane of TECHIE existence, the year must be split in two: 6 months of plenty, following the delivery of Gaffa unto the TECHIES, and 6 months of famine, when the Gaffa must surely run out.

\section{The Gospel according to Luke}
Our amps are switched off \\
The Cans are not patched into the PA \\
The Masters are down. \\
The loudspeakers are disconnected \\
THEY CAN'T HEAR YOU!\\

\section{The Book of Bill}
And when God had created light, and sets, and props, and costumes, and the like, God rested, and this sabbath day he named the Cast Party. And the Cast Party was good. But on the morning following this said sabbath, the Lord did rise with pain of head and nausea of stomach, and God did go forth into the lighting booth to take unto himself some Pain-Aid and Pepto from the first-aid kit. And because the Lord had not yet drunk of his heavenly goblet of black coffee, he thought, "I shall make a creature in my likeness, and in the likeness of the Techies, who are already in my likeness, and all shall bring me glory." And God took a handful of Pain-Aid and Pepto and created a being in his likeness, and the likeness of the Techies, wearing many tools and garments of only black. And God saw that his creation was good, and firm of joint, and could see in the dark. 

And the Techies did party, and build the new creature a beautiful set in which to dwell, with perfect sight lines, a lowering grid, a turntable, three scrims, showers in the back, and gelchangers in the lights. And God said, "My child, I name thee Bill. Go forth and play, Bill." Bill did go forth and play, and henceforward a being running forth like a child on a set would be called a Play. And God said only, "Run, play, and be fruitful; live in great peace on this beautiful set which my Techies have created. Only heed one warning: thou shalt not play pridefully in the vision of anyone, with the exception of the Techies, who are always watching and well should be."

Bill did play for many nights alone with no one but the Techies for company, and was content. But each time God did fade the sunset special from the western side of the theater, Bill's heart cried more and more in torment. And Bill wept to God, "Lord God who hath created me, who hath clothed me and fed me and taught me the holy ways of wrenches and circuits and hath not troubled me to climb any really tall ladders, Lord God, I am lonely and need another like myself." And the Lord was moved to pity. So he took a pipe wrench and smote Bill upside the head, then clipped a lock of his flaxen hair with a utility knife. He mixed this with some sawdust and two measures of joint compound. And God did stir. He stirred until the grid did quake and the heavens flickered. Thus was created another being in the likeness of Bill, but suave of build and of hair as blonde as the morn. God said to Bill, "My son, I offer you the great honor of bestowing this fine creature a name." "I name him Steve," Bill replied with stars in his eyes.

Thusly became Bill and Steve playmates, and there was much frolic and rejoicing on the set. And God saw that they were good, and was not moved to concern. But Bill and Steve grew fond of their games of charades, and were less and less satisfied with the clear, alert gaze of the Techies. "I want not to be gazed upon merely for my light cues," cried out Bill in great distress. "Ah, and I am such a handsome devil," sighed Steve, admiring his reflection in the lid of a paint can. "What a pity that such beauty should go unappreciated!" And God did shake his great head and chuckle, unconvinced that any of his children should go astray.

One night, when the R78's glowed softly in the fresnels, Steve was stirred to waking by a strange noise. He noticed a shadowy figure standing before him. "Speak, and proclaim thyself!" Steve insisted, leaping to his feet and grabbing a piece of stage artillery from the nearby prop table. "Fear me not," proclaimed the specter. "I am none but a weary traveler, and I have journeyed from afar merely to perceive thy beauty and talent." "You're kidding," quoth Steve, dropping his sword. "Ah, indeed," the figure did continue, "far and wide hath the news spread of thy ability to behave in the likeness of characters other than thyself." Steve replied, "And I thought it was simple schizophrenia!" with some relief. And the figure did pull forth a business card, and when Steve did inquire as to what meant the strange word "agent," the figure replied that he was none but a human being who appreciated a good performance and liked to see other people appreciate it, too. For a small fee, of course.

Steve did act for the agent, and tap dance, and sing, paying no heed to the word of God. The agent brought in some of his family, then friends, and Steve awoke Bill to play a jazzed-up duet of "Don't Cry For Me Argentina" fit to make Patti weep. And the Techies did follow Bill and Steve with large round lights, and adjust the sound as necessary, for they understood the word of God and were bound by their God-betrothed duty. The audience did pound their palms together in applause like unto thunder, standing and whistling and shouting for an encore. God was thus awakened from his slumber.

Bill and Steve were aware of the coming wrath of God, and they ran and hid. God sent forth all the Techies to find them.When the Techies did return, they had retrieved not only Bill and Steve but armloads of 8x10 headshots from the lobby and empty bottles of mineral water from the green room. Bill and Steve did cower before God. And God said: Henceforward shalt thou be called "actor," And all thy descendants "actor" as well. Thou shalt wear colorful clothes, And be stripped of the holy knowledge of the Techie. May you marry many times without success. May the tabloids exploit you. May you die lonely deaths in hotel rooms in Vegas, For thou hast fallen from grace. Bill and Steve wept and cried out for redemption, but it was to no avail, for they had sinned in the eyes of God. 44 And their garments became colorful, and sewn with sequins, and uncomfortable, and their faces coated in pancake makeup. And they did forget all that they were taught about being a good Techie, and needed to be spoken to in small words, and could not see even glo-tape in the dark. And the Techies prevailed.

\section{The Birth of a Techie}
And lo a parcan in yonder western sky,did shine with `152' light. The nieve Fresher was attracted to its golden glow but alas there was no room at the proj. box."Try the rostra store where ye may well be able to find a place among the old damp sets of yesteryear."so the fair techie child arrived at the portal to the lowly store and stepped through to find its techie parents who had returned for freshers week. The fresher was quickly converted to techieism and began uttering the sacred words of `gaffa',`AJ' and `lecky' were among the prononcements. 

And low on the second day three members of the ruling party of techie land did arrive bearing gifts of wonderment.

The first bought the backstage pager for communication is the second most holy virtue. 

The second wearing a cape of black velvet bought the sacred roll of gaffa for no techie can be truly fulfilled without the wonderment of the gaffa. 

The third addorned in strange headwear bought a strange cable which he described as "shedloads of these to shedloads of these." 

The techie was truly amazed and grateful. 

The three then left but not before promsing full and comprehensive training tyo all new fresher techies. 

At this the techie parents could bare the silence no longer and burst into tears. 

On the third day three more wise men/persons arrived. 

Instead of gifts they bought pearls of wisdom. 

The first,the director,spoke of the promised land,"One day you shall enter the promised land,the new theatre will be completed." 

The second spoke of the treatment of lowly things,"Dont drag the chairs across the floor." 

tem The third and finally visitor just stood there in silence for the masters were down and the amps were turned off. So no-one could hear St luke offer to buy a round of drinks

\section{Parable of the Lighting Desk}
Low the story begind one night after a gig at UBSA(A temple of disco) 

The techies had performed remarkably during the performance of dancing by the lowly actors and now the disco had begun.The techies stood in a huddle and the techie director said "ERRRRRR!!!!"with a wave of the hands, and from this one gesture they knew it was time for a break before the night of a thousand de-rigs. 

But they stopped at the portal of the mighty UBSA temple the techie director speaketh, "what about the truly wonderous lighting desk,might not somebody half-inch it." 

And Chris and Dave replied as one "who would be mad enough to steal a lighting desk." With these immortal words they parted into the cold night air having agreed to meet back at eleven. 

As the witching hour aproached the techie director and his assistant felt the desk call and found themselves before the ancient doors of UBSA,but the insignificant audience were still partying and little could be done. having looked around for a job we were held in holy wonderement from the green twinkle of the lighting desk. Strangly drawn they took its carry case and packed it into its holy foam.the sound desk also called although its voice was old and worn but it was taken into our arms and we took them both home. 

On returning to the temple of UBSA we sat in a corner waiting for the music to abate. 

Then movementt caught our eye Chris and Dave had returned,they were performing strange gestures, then we hear again the "errr!!" and we knew they were unaware of the safety of the desk. 

at this knowledge they panicked with flailing arms and whimpers of pain they searched,but the desk was nowhere,they asked two passersby where the desk was and they mockingly said,"two blokes from the night club came and knicked it." 

So Chris did panick some more and went to consult the DJ but the oracle could not answer. 

Just as they were about to give up they saw the sniggering forms of the directors in the corner and then they went ballistic and threatened to kill them by depriving them of the holy gaffer tape. 

And the moral of this story, always find the techie director for he shall have the equipment.

\section{The Ten Tech Commandments}
\begin{enumerate}
\item Love thy gaffer tape as thou would love thyself.
\item Honour thy stage manager and thy director.
\item Thou shalt not get caught in light.
\item Thou shalt not talk louder than a whisper.
\item Thou shalt not covet another techies headset / torch / t-shirt.
\item Thou shalt not drop things from the gyro / catwalk.
\item Thou shalt not crave sustenance other than caffeine and sugar.
\item Thou shalt not kill another techie. Actors not inclusive.
\item Thou shalt assist the actor when walking through the wings of darkness.
\item Thou shalt be as God like as possible - fast, quiet, efficient.
\end{enumerate}

\section{The Plan}
In the beginning there was the Plan.

And then came the Assumptions.

And the Assumptions were without form.

And the Plan was without substance.

And darkness was upon the face of the Techies.

And they spoke amongst themselves saying, 'It is a crock of shit and it stinketh.'

And the Techies went to the Stage Manager and said, 'It is a pile of dung, and none may abide by the odor thereof.'

And the Stage Manager went unto the Production Manager saying, 'It is a container of excrement, and it is very strong, such that none may abide by it.'

And the Production Manager spoke amongst the Directors saying, 'It is a vessel of fertilizer, and none may abide by its strength.'

And the Directors went unto the Producers saying one to the other, 'It contains that which aids plant growth, and it is very strong.'

And the Producers then went to the Backers saying unto them, 'It promotes growth and is very powerful.'

And the Backers sent forth the publicity saying unto the Public, 'This new plan will actively promote the growth and vigor of the production, with powerful effects to be felt all the way to the audience!!!'

And the Public looked upon the Plan and saw that it was good.

And the Plan became Policy.

And the Techies looked upon the Policy and saw that it was nothing but the same old shit with a new name.

And thus, shit happens

\end{document}